A supertree pipeline for summarizing phylogenetic and taxonomic information for millions of species

### 2017-01-23 doc/paper1-submission/paper5.tex
Add section on MRP and MinCut.

% TODO: add stuff to paper
% R1.2 Mention that applying ranks to trees instead of nodes is problematic.
%      Mention transparency?
% R2.1: Add paragraph mentioning MRP, MinCut, and how they are different. - 1.1.6

@@

We also consider matrix representation with parsimony (MRP) and MinCut.
MRP can display edges not found
in any input tree, and so fails criterion \#1.  MRP is used in many
studies that attempt to infer the true tree from a lot of input
trees.  To some extent, MRP tries to treat each tree as data, which
differs from our approach here.
MinCut (and Modified MinCut) attempts to favor relationships present
in multiple input trees during conflict resolution.
Both MRP and MinCut attempt to adjudicate conflicts in a way that
favors relationships present in more input trees.  Thus, they perform
something more like a weighted average.  However, the reason the
supertree resolves conflicts in a particular way is not clear and
transparent, and does not allow a method for curators to adjust the
supertree.

A number of other supertree methods exist, including Matrix
Representation with Parsimony (MRP) and MinCut.  MRP
% http://currents.plos.org/treeoflife/article/reweaving-the-tapestry-a-supertree-of-birds/
MRP - displays unsupported groups (\#1), not rank-based (\#2), ?
SuperFine - computes a strict consensus, then MRP
Minimum Flip - 
(Modified) MinCut -

>>>>

@@

Matrix Representation Parsimony (MRP) is one of the
most widely used supertree approaches \citep{baum1992combining,BinindaEmonds2007b,Davis2014}.
MRP attempts to encode branches of input trees as characters in a data
matrix, and then find an optimal tree according to the maximum
parsimony criterion. Such an approach does not provide a clear and transparent
explanation for including particular edges in the supertree.
MRP can also infer edges that exist in none of the input trees, which 
violates our Goal \#1 \citep{gatesy2004critique}.

Another commonly used method is MinCut \citep{semple2000supertree} or
Modified MinCut \citep{page2002modified}.  Like our approach, MinCut
is based on the BUILD algorithm \citep{AhoSSU1981}.  However, MinCut deals
with conflicts by modifying the BUILD algorithm to resolve
incompatibilities by discarding edges that are present in the smallest 
number of input trees.  This approach thus violates our Goal \#2 of
resolving conflict via ranks that can be altered by a curator to
influence the output tree.
